\documentclass{brian_ats}
\begin{document}
\name{Neema Nyakara Ogega}
\contact{+254 706 551 538}{neemaogega@gmail.com}{62000 - 00200 JKUAT, Nairobi}
\section{summary}
I started my career as a health record assistant trainee at a small district hospital in Kisii county; this is where I first interacted with production data in kenyaEMR. Over the years, I have seen my level of interests and skills in data management grow. I have worked with DHIS2, REDcap, and I often use excel a lot in my current role. I would love deeply immerse myself in a more challenging environment and to advance my skill set in data management.


%at a small district hospital 
%as a health records officer in 

%My 2.5 years experience, combined with a broad set of technical skills in research and data management have helped many innovate and achieve greater value in often limited settings. Over the years, I have gained increasing interestt with 

 %the best health device innovator at makerspace. Our project  
%I was part of the 2019 award winner of the Health Device Innovator at Makerspace where we came up ...., I desire to take up new challange, learn and advance 

%(DHIS2, RedCup and KenyaEMR) have helped many achieve greater results in a timely fashion.

%data collection and management tools (like DHIS2, RedCup and KenyaEMR) have helped me grow and cultivate a greater interest in data. 

%have been a great journey of learning and to further advance 

%, management and reporting tools (DHIS2, RedCup and KenyaEMR) provides 

%I have about 2.5 years hands on experience in open source data collection, management and reporting tools  -  DHIS2, RedCup. and Keny EMR. 


%My 2.5 experience has helped me develop skills on data management.  I have  gained insights on database and record-keeping, generation of monthly data reports a nd handling of different types of data. 

%I  aim to deliver the same efficient  results and continual improvement on myself. 
\section{Employment History}
\datedsubsection{Makerspace, (Nairobi, U.o.N Kabete Campus)}{APRIL  2019 -- PRESENT}
\subsubsection{Health Devices Researcher - Intern}
\begin{itemize}
    \item Lead focus group discussions \& key informant interviews on postpartum hemorrhage (PPH).
    \item Design, develop \& administer survey questionnares for data collection and project reporting.
    \item Analyze \& provide insights on PPH to continuously inform the development of health devices.
    \item Train, orient \& support healthcare providers and on use of the newly developed medical devices.
    %- non-pneumaticanti-shock  garments.
\end{itemize}

%\employmenthistory
%{ If this experience is in the present then start your bullet points with strong present verbs}
%{If this experience is in the past then start your bullet points with strong past verbs}
%{ Make sure each line is tangible and the value you delivered can be easily perceived}
%{ Be consistent with regards to length of sentence, ideally they should be one line each}
%{ If you decide to have two lines per bullet point don’t finish the second line with one word}
%{Try to have your past experience match the job descriptions of the roles you are applying for}
%{ Your past experience should match in terms of number of bullet points to look consistent}
%{ Make sure your punctuation and grammar are also consistent throughout your resume}

\datedsubsection{Ministry of Health (U.o.N, Chiromo Campus)}{APRIL 2018 -- SEPTEMBER 2018}
\subsubsection{Health Informatics Bootcamp Participant}
\begin{itemize}
    \item Trained on the development of the Kenya Health Management Information System (KeHMIS).
    \item Able to use DHIS2, the KeHMIS  to generate reports \& dashboards for use by program teams.
    \item Developed \& further enhanced documentation of the Kenya  Master Health Facility List (KMHFL).
    \item Oriented on the Kenya eHealth landscape, tools and standards for interoperability \& data exchange. 
\end{itemize}
\datedsubsection{Nyamache Sub County Hospital (Kisii, Nyamache)}{APRIL 2017 -- SEPTEMBER 2017}
\subsubsection{Health Records Assistant}
\begin{itemize}
   \item Orientation on the MOH standard paper forms \& digital tools for data collection and reporting.
   \item Experience on using Kenya EMR to register and manage patients records for HIV/TB reporting.
   \item Assited in the billing of patient records and hospital charges through NHIF \& other health insurance. 
   \item Assited in the filing, indexing and coding of patient diseases for better management of patient records.
\end{itemize}

%\subsubsection{Title - Something Impactful}
\section{Relevant skills}
Ability to work in fast paced environment, \\*
Communication \& presentation skills, \\*
R for statistical computing, \\*
Excel for analysis, \\*
REDCap for health research surveys\\*

\section{Other Interests}
Travelling, Reading and learning something new.
\section{Languages}
English, Kiswahili and Kisii
\section{Education}
\institution{BSc. Health Records \& Information Management}{JKUAT}{Juja}{2019}

\section{Referees}

Mr. Dennis Banga,\\*
Senior SoftwareDeveloper,\\*
Health Informatics for Kenya, \\*
dennisbanga@gmail.com\\*
Tel: 0724015053, Nairobi.\\*\\*
\noindent
Mr. Derrick Mugasia, \\*
Assistant Project Manager, \\*
University of Nairobi, \\*
nagide@uonbi.ac.ke, \\*
Tel: +254 723 950 037, Nairobi.\\*\\*
\noindent
Mr. Maxwel Kibari,\\*
Senior Health Record Officer,\\*
Nyamache Subcounty Hospital,\\*
maxkibari@gmail.com,\\*
Tel: +254 704256168, Kisii

\end{document}